The Splashback Radius of Planck-SZ clusters

### 2018-09-13 RSP_Report/RSP_Report_v2.tex
Newly initialized repo

\pdfoutput=1
\documentclass[iop, apjl, twocolappendix, numberedappendix]{emulateapj}
%\usepackage{newtxtext,newtxmath}
\usepackage[T1]{fontenc}
%\usepackage{ae,aecompl}
\usepackage{float}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{txfonts}
\usepackage{ulem}
\usepackage{xspace}
\usepackage[colorlinks=true,urlcolor=blue,linkcolor=blue,citecolor=blue]{hyperref}
%\usepackage{nccmath}
\usepackage[utf8]{inputenc}
\newcommand{\fhat}[1]{\expandafter\hat#1}
\newcommand{\fbar}[1]{\expandafter\bar#1}
\newcommand\fnurl[2]{%
  \href{#2}{#1}\footnote{\url{#2}}%
}
\def\rs{r_{\rm s}}
\def\rhos{\rho_{\rm s}}
\def\se{s_{\rm e}}
\def\ftrans{f_{\rm trans}}
\def\rhog{\rho_{\rm g}}
\def\rhoginner{\rho_{\rm g}^{\rm inner}}
\def\rhogouter{\rho_{\rm g}^{\rm outer}}
\def\rt{r_{\rm t}}
\def\rout{r_{\rm out}}
\def\mpch{h^{-1}{\rm Mpc}}
\def\msunh{h^{-1}{\rm M_{\odot}}}
\shorttitle{Splashback radius of Planck-SZ clusters}
\shortauthors{Zürcher, More}

@@

\author{
Dominik Zürcher \altaffilmark{1, 2}
Surhud More \altaffilmark{1, 3}, 
}
\affil{
$^{1}$Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), \\ 
$^{2}$Department of Physics, ETH Zurich, Wolfgang Pauli Strasse 27, 8093 Zurich, Switzerland\\
$^{3}$The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa, Chiba 277-8583\\
}

\begin{abstract}
We present evidence for the existence of the splashback radius
in galaxy clusters selected using the Sunyaev-Zeldovich effect.
We show that the deprojected cross-correlation of galaxy clusters
found in the Planck survey with galaxies detected photometrically in
the Pan-STARRS survey, shows a sharp steepening feature (a
logarithmic slope steeper than $-3$), which we associate with the
splashback radius.  We infer the three-dimensional splashback radius
for the SZ cluster sample to be $r_{\rm sp}=1.81_{-0.33}^{+0.28}$ $\mpch$,
where the cluster sample has an average halo mass $M_{\rm
500c}=3.0\times10^{14}\msunh$ at an average redshift of $z=0.18$.
The inferred value of the splashback radius is consistent with the
expected location for dark matter halos in the standard cold dark
matter paradigm. However, given the limited precision of our
measurements, we cannot conclusively rule out the smaller splashback
radius measured so far in the literature for photometrically
selected galaxy clusters. We show that the splashback radius does
not depend upon the galaxy magnitude for galaxies fainter than
$M_i-5\log h=-19.44$, and is present at a consistent location in
both red and blue galaxy populations. The presence of the splashback radius in
color-separated galaxy distributions could potentially be used to put lower limits on the
quenching timescales for galaxies. Further, we record a strong increase 
in the fraction of red galaxies that is associated with the splashback radius.

@@

@@

@@

@@

    \begin{tabular}{ccccccccccc}

@@

    & $\log_{10}(\rho_{\mathrm{s}})$ & $\log_{10}(\alpha)$ & $\log_{10}(r_{\mathrm{s}})$ & $\rho_0$ & $s_{\mathrm{e}}$ & $\log_{10}(r_{\mathrm{t}})$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ & $f_{\rm min}$ & $\sigma$\\ 

@@

    Prior Type & None & Normal & Flat & None & None & Flat & Normal & Normal & Normal & Normal\\ 

@@

    Prior Range & - & $\log_{10}(0.2)| 1.2$ & [0.1,5.0] & - & - & [0.1,5.0] & $\log_{10}(6.0) | 0.4$ & $\log_{10}(4.0) | 0.4$ & $0.15 | 0.21$ & $0.41 | 0.3$\\

@@

We restrict ourselves to the redshift range $0.03 \leq z \leq 0.33$
in order to mimic the redshift range used by
\citet{more2016detection}. Due to the large beam size of the Planck
satellite, the cluster positions as reported in the catalog may be
mis-centered from the true centers of the galaxy clusters. We perform
a visual inspection of Pan-STARRS images taken around the detected
galaxy clusters in order to locate the nearest, brightest cluster
galaxy (BCG). We regard the position of the BCG as the true cluster
location, under the assumption that the BCG is located at the true,
gravitational center. Due to this crude assumption, we additionally 
include the effects of a possible, remaining mis-centering of the 
cluster positions in our model for the two-dimensional correlation 
function (see Section~\ref{sec:mis-centering}). 
The final sample that we use consists of 596
galaxy clusters and is about an order of magnitude smaller compared
to the sample used in \citet{more2016detection}. The sample we use
in this paper has an average redshift of 0.177, and an average
cluster mass $M_{500c}$ of about $3.0 \cdot 10^{14}
h^{-1}$M$_{\sun}$. In Table~\ref{tab:cluster_catalogs} we compare
the main properties of the cluster catalog used in this work to that
used by \citet{more2016detection}. The sky positions of the clusters
can be found in Figure~\ref{fig:planck_fig} in
Appendix~\ref{sec:figures}.

@@

We use the functional form of \citet{diemer2014dependence} in order
to model our two-dimensional correlation function measurements. This
functional form consists of an inner Einasto profile and an outer
power law profile connected by a smooth transition
\begin{align}
\xi_{\rm 3D}(r) &= \rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r) + \rho_{\mathrm{out}}(r)\,, \\
\rho_{\mathrm{in}}(r)&=\rho_{\mathrm{s}}\exp\left( -\frac{2}{\alpha}\left[ \left( \frac{r}{r_{\mathrm{s}}}\right)^{\alpha}-1 \right] \right)\,,\\
\rho_{\mathrm{out}}(r)&=\rho_{\mathrm{0}}\left( \frac{r}{r_{\mathrm{out}}}\right)^{-s_{\mathrm{e}}} \,,\label{eq:model} \\
f_{\mathrm{trans}}(r)&=\left( 1+\left( \frac{r}{r_{\mathrm{t}}} \right)^{\beta} \right)^{-\gamma/ \beta}\,,
\label{eq:dk14}
\end{align}
where $r$ indicates the three-dimensional radial distance from the
halo center \citep{diemer2014dependence}. We model the
two-dimensional correlation function, $\xi_{\rm 2D}$ as an integral
over the three-dimensional correlation function
\begin{equation}
\xi_{\rm (2D,0)}(R)=\frac{1}{R_{\rm max}}\int^{R_{\mathrm{max}}}_0 \xi_{\rm 3D}(\sqrt{R^2+x^2}) dx \,
\label{eq:surface}
\end{equation}
where we adopt $R_{\mathrm{max}}=40$ $h^{-1}$Mpc for the maximum projection
length. Variations of this length do not change the location of the
splashback radius appreciably as tested in
\citet{more2016detection}. The functional form adopted in
Equation~\ref{eq:dk14} has nine model parameters,
$\rho_{\mathrm{s}}, \alpha, r_{\mathrm{s}}, r_{\mathrm{out}},
\rho_{\mathrm{0}}, s_{\mathrm{e}}, r_{\mathrm{t}}, \beta$ and
$\gamma$. Given the perfect degeneracy between the parameters
$r_{\mathrm{out}}$ and $\rho_{\rm o}$, we fix $r_{\mathrm{out}}=1.5$ $
h^{-1}$Mpc.

\paragraph{Modelling cluster mis-centering}
\label{sec:mis-centering}
Mis-centering of the central cluster positions can heavily affect 
the small-scale correlation function on scales smaller than the typical mis-centering distance. 
Although, the splashback radius is located at much larger scales, 
the change of the inner part of the correlation function can alter the model fit significantly. Mis-centering effects are not expected to change the location of the splashback feature but they can in principle decrease the significance of the evidence for the splashback feature \citep{baxter2017halo}.

The mass dependence of the exact mis-centering fractions are not
well understood and mis-centering effects are therefore difficult to model \citep{Skibba:2011, Hoshino:2015}. We follow the approach outlined in \citet{baxter2017halo} to take the effects of a possible mis-centering of a fraction of the cluster positions 
into account by modelling the influence on the two-dimensional correlation function.

Denoting the fraction of mis-centered clusters in the sample with $f_{\rm mis}$ we relate
the correlation function $\xi_{\rm 2D}(R)$ that is affected by the mis-centering of the clusters to the correlation function
unaffected by mis-centering $\xi_{\rm (2D,0)}(R)$ by

\begin{equation} 
\xi_{\rm 2D}(R) = (1-f_{\rm mis})\xi_{\rm (2D,0)}(R)+f_{\rm mis}\xi_{\rm (2D,mis)}(R)
\label{eq:full}
\end{equation}

where the contribution of the mis-centered clusters to the correlation function is captured by $\xi_{\rm (2D,mis)}$. 
We model the mis-centered component $\xi_{\rm (2D,mis)}$ as

\begin{equation}
\xi_{\rm (2D,mis)}(R)=\int_0^\infty \mathrm{d}R_{\rm mis} P(R_{\rm mis})\xi_{\rm (2D,mis)}(R|R_{\rm mis})
\end{equation}

where we assign a probability $P(R_{\rm mis})$ that a cluster is mis-centered by a comoving distance $R_{\rm mis}$.
The contribution $\xi_{\rm (2D,mis)}(R|R_{\rm mis})$ from a cluster mis-centered by a distance $R_{\rm mis}$ 
relates to the unaffected correlation function $\xi_{\rm (2D,0)}$ as

\begin{equation}
\xi_{\rm (2D,mis)}(R|R_{\rm mis})=\int_0^{2\pi}\frac{\mathrm{d}\theta}{2\pi}\xi_{\rm (2D,0)}\left(\sqrt{R^2+R_{\rm mis}^2+2RR_{\rm mis}\cos{\theta}}\right)
\end{equation}

according to \citet{yang2006weak} and \citet{johnston2007cross}. Following \citet{simet2016weak} we model the mis-centering probability 
$P(R_{\rm mis})$ as a Rayleigh distribution:

\begin{equation}
P(R_{\rm mis})=\frac{R_{\rm mis}}{\sigma^2}\exp{\left( -\frac{R_{\rm mis}^2}{2\sigma^2}\right)}
\end{equation}

Therefore, the mis-centered contribution is fully characterized by the two parameters $f_{\rm mis}$ and the witdh 
of the mis-centering probability distribution $\sigma$.
\newline

We cross-match our SZ selected cluster sample with the X-Ray selected ACCEPT cluster sample \citep{cavagnolo2009vizier}.
Assuming the ACCEPT clusters to lay at the true gravitational cluster centers we construct Gaussian priors
for the two mis-centering model parameters $f_{\rm mis}$ and $\sigma$ from the comparison of the 
two samples. The central values as well as the scales of the priors are listed in Table~\ref{tab:priors}.

Including mis-centering our model is described by ten model parameters.
We infer the posterior distributions of those parameters by fitting the model for the two-dimensional correlation
function affected by mis-centering to the measured two-dimensional correlation signal. 
We use the affine invariant Markov Chain Monte Carlo sampler of \citet{goodman2010ensemble} as
implemented in the parallel python package {\it emcee} by
\citet{foreman2013emcee}. We adopt priors similar to
\citet{more2016detection} on some of our parameters based on the
expectations of their values from numerical simulations, but double
the scales of the normal priors compared to their work (see
Table~\ref{tab:priors}). The central value for the prior on $\alpha$
is deduced from mass estimates \citep{gao2008redshift}, whereas the
central values on the priors of $\beta$ and $\gamma$ were
recommended by \citet{diemer2014dependence}.

@@

\subsection{Separation of red and blue galaxies}
\label{sec:Color}

>>>>

\pdfoutput=1
\documentclass[iop, apjl, twocolappendix, numberedappendix]{emulateapj}
%\usepackage{newtxtext,newtxmath}
\usepackage[T1]{fontenc}
%\usepackage{ae,aecompl}
\usepackage{float}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{txfonts}
\usepackage{ulem}
\usepackage{xspace}
\usepackage[colorlinks=true,urlcolor=blue,linkcolor=blue,citecolor=blue]{hyperref}
%\usepackage{nccmath}
\usepackage[utf8]{inputenc}
\newcommand{\fhat}[1]{\expandafter\hat#1}
\newcommand{\fbar}[1]{\expandafter\bar#1}
\newcommand\fnurl[2]{%
  \href{#2}{#1}\footnote{\url{#2}}%
}
\def\rs{r_{\rm s}}
\def\rhos{\rho_{\rm s}}
\def\se{s_{\rm e}}
\def\ftrans{f_{\rm trans}}
\def\rhog{\rho_{\rm g}}
\def\rhoginner{\rho_{\rm g}^{\rm inner}}
\def\rhogouter{\rho_{\rm g}^{\rm outer}}
\def\rt{r_{\rm t}}
\def\rout{r_{\rm out}}
\def\mpch{h^{-1}{\rm Mpc}}
\def\msunh{h^{-1}{\rm M_{\odot}}}
\shorttitle{Splashback radius of Planck-SZ clusters}
\shortauthors{Zürcher, More \& Refregier}
\slugcomment{Master's Thesis:
In partial fulfillment of the requirements for the Master of Science ETH in Interdisciplinary Sciences}

@@

\author{
D. Zürcher \altaffilmark{1, 2}
Surhud More \altaffilmark{2, 3, 5}, 
A. Refregier \altaffilmark{4, 6}
}
\affil{
$^{1}$Department of Chemistry and Applied Biosciences, ETH Zurich, Vladimir-Prelog-Weg 1, 8093 Zurich, Switzerland;{\tt dominikz@student.ethz.ch}\\
$^{2}$Kavli Institute for the Physics and Mathematics of the Universe (Kavli IPMU, WPI), \\ 
${^3}$The University of Tokyo, 5-1-5 Kashiwanoha, Kashiwa, Chiba 277-8583\\
$^{4}$Department of Physics, ETH Zurich, Wolfgang Pauli Strasse 27, 8093 Zurich, Switzerland\\
${^5}$Supervisor\\
${^6}$Co-supervisor\\
}

%\pubyear{2018}

%\begin{document}
%\label{firstpage}
%\pagerange{\pageref{firstpage}--\pageref{lastpage}}
%\maketitle

\begin{abstract}
%Being a unique observational probe for the mass accretion rate of
%dark matter halos the splashback radius has been well-modeled by the
%use of numerical simulations. However, although its signature has
%been found using optical cluster catalogs, discrepancies from the
%simulations were noted and the plausibility of the detections were
%questioned. We overcome those caveats by using SZ selected clusters
%from the Planck survey. By cross-correlation with galaxies from the
%Pan-STARRS survey we construct the two-dimensional galaxy cluster -
%galaxy cross-correlation signal. We detect a clear steepening in the
%signal, which is steeper than $-3$ and poorly modeled by the NFW
%profile. The feature is found at a location consistent with the
%expectations. The uncertainty on the location of the splashback
%radius is recorded as $\sim 15$\%. We also study the
%cross-correlation of red and blue galaxies, separately and find
%evidence for the existence of the splashback feature in both
%populations. Further, we record a strong increase in the fraction of
%red galaxies that is associated with the splashback radius.

We present evidence for the existence of the splashback radius
in galaxy clusters selected using the Sunyaev-Zeldovich effect.
We show that the deprojected cross-correlation of galaxy clusters
found in the Planck survey with galaxies detected photometrically in
the Pan-STARRS survey, shows a sharp steepening feature (a
logarithmic slope steeper than $-3$), which we associate with the
splashback radius.  We infer the three-dimensional splashback radius
for the SZ cluster sample to be $r_{\rm sp}=1.85_{-0.30}^{+0.26}$ $\mpch$,
where the cluster sample has an average halo mass $M_{\rm
500c}=3.0\times10^{14}\msunh$ at an average redshift of $z=0.18$.
The inferred value of the splashback radius is consistent with the
expected location for dark matter halos in the standard cold dark
matter paradigm. However, given the limited precision of our
measurements, we cannot conclusively rule out the smaller splashback
radius measured so far in the literature for photometrically
selected galaxy clusters. We show that the splashback radius does
not depend upon the galaxy magnitude for galaxies fainter than
$M_i-5\log h=-19.44$, and is present at a consistent location in
both red and blue galaxy populations. The presence of the splashback radius in
color-separated galaxy distributions could potentially be used to put lower limits on the
quenching timescales for galaxies. Further, we record a strong increase 
in the fraction of red galaxies that is associated with the splashback radius.

@@

%The interpretation of the dependence on accretion rate is straightforward and can be explained by the dynamics of a dark matter particle falling down and subsequently climbing out of a changing potential well of the dark matter halo. The dark matter particle will gain kinetic energy as it falls down the potential well. However if the potential well grows during this time, then the particle does not have enough energy to climb out of it. This results in the reduction of the apocenter of its orbit, and hence the splashback radius. The faster the accretion rate, the deeper the potential well gets, the smaller the splashback radius.

@@

%The correct interpretation of observations of large scale structures in the universe requires accurate, theoretical predictions for the structure of dark matter halos as they form in a cold dark matter scenario. Therefore, a large efford has been made in the past decades to predict the density profiles of dark matter halos starting with \citet{gunn1972infall} who used a simple top hat model to describe the collapse of the halos. However, cosmolgical simulations revealed that the collapse of the halos are rather triaxial than spherically symmetric and therefore more complicated than expected \citep{klypin1983three}. The NFW profile named after its inventors \citet{navarro1997universal} became one of the most popular models taking into account the triaxial nature of the collapse. It was found that the profiles of dark matter halos exhibit a monotonical steepening at larger radii \citep{huss1999universal}. This behaviour is badly described by the NFW profile which inherits an asymptotic slope of -3 at large radii, since \citet{navarro1997universal} focused on the description of the inner part of the dark matter halos. Instead, a more accurate desription has been found through the Einasto profile (e.g., \citep{navarro2004inner}).
%Most of the studies on dark matter halo profiles focused on the inner regions of halos since these are more easily probed by the observable galaxy distributions (e.g., \citep{moore1999dark}). However, through X-Ray and Sunyeaev-Zeldovich surveys as well as weak gravitational lensing studies the mass distribution of the outskirts of the halos become more and more accesible \citep{diemer2014dependence}. Therefore, \citet{diemer2014dependence} investigated the outer regions of the dark matter halos in order to provide more accurate models for the description of the outskirts of the halos which are necessary for the correct interpretation of such observations. They showed, that the classical fitting functions such as the NFW or the Einasto profile fail to describe the outer parts of the mass profiles as inferred from N-body simulations. Particularly they found a sharp steepening of the profile around the virial radius $r \approx r_{\mathrm{200m}}$, which is not modeled correctly by those fitting functions and they argue that the local steepening is caused by a caustic formed by recently accreated particles which passed through the pericenter of their orbit just once since their infall onto the cluster. They proposed a new fitting function consisting of an inner Einasto profile and an outer power law profile connected by a smooth transition
%\begin{align}
%\rho(r) &= \rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r) + \rho_{\mathrm{out}}(r)\,, \\
%\rho_{\mathrm{in}}(r)&=\rho_{\mathrm{s}}\exp\left( -\frac{2}{\alpha}\left[ \left( \frac{r}{r_{\mathrm{s}}}\right)^{\alpha}-1 \right] \right)\,,\\
%\rho_{\mathrm{out}}(r)&=\rho_{\mathrm{0}}\left( \frac{r}{r_{\mathrm{out}}}\right)^{-s_{\mathrm{e}}} \,,\label{eq:model} \\
%f_{\mathrm{trans}}(r)&=\left( 1+\left( \frac{r}{r_{\mathrm{t}}} \right)^{\beta} \right)^{-\gamma/ \beta}\,,
%\label{eq:dk14}
%\end{align}
%where $r$ indicates the three dimensional radial distance from the halo center \citep{diemer2014dependence}.

%In a follow up study \citet{adhikari2014splashback} derived a simple theoretical model from first principles explaining the presence of the local steepening found by \citet{diemer2014dependence}. They base their work on the ideas developed by \citet{diemer2014dependence} and \citet{fillmore1984self}. They argue that caustics arise in triaxial collapses of dark matter due to a pile up of the orbits of multiple particles at a similar radius. Such caustics most frequently appear close to the apocenters of the orbits due to the radial velocity being very small at that point, which causes the particles to spend a longer time there \citep{lithwick2011self}. The outermost caustic of a halo is associated with the first apoapsis of the most recently accreted particles. Those particles underwent a first collapse meaning that they passed through the center of the halo just once. This phenomenon is termed splashback effect and the radius corresponding to the density drop after the outermost caustic has been named splashback radius correspondingly.

%The location of the splashback radius strongly depends on the accretion rate $\Gamma$ of the halo. The interpretation of the dependence on $\Gamma$ is straightforward: Imagine a dark matter particle which passed through the center of the halo just once and is on its way back towards larger radii. If the gravitaional potential of the halo would be static the particle would inherit enough kinetic energy to climb the potential and leave the halo again. However, since the halo keeps on accreating matter while the particle moves away from the center, its gravitational potential well deepens and the dark matter particle will not be able to climb the potential completely but instead "splashes back" towards the center of the halo. The deepening of the potential during the particle's journey depends on the amount of the accreated material and therefore on the value of $\Gamma$. Hence, a larger $\Gamma$ leads to a smaller splashback radius. This means that the location of the splashback radius can be used to infer the accretion rate of a halo \citep{adhikari2014splashback}

%Similarly, the redshift dependence arises through the influence of the values of the cosmological paramerters $\Omega_m$ and $\Omega_{\Lambda}$ on the amount of material that can be accreated onto the halo during the time that the particle requires to travels outwards from the center again. At lower redshifts $\Omega_m$ decreases quickly as $\Omega_{\Lambda}$ becomes more dominant. Therefore, the mean background density $\bar{\rho}_m$ of the universe decreases quickly as well and the halo can only accreate less and less material which slows down the deepening of the potential well and increases the splashback radius \citep{adhikari2014splashback}.

%Motivated by the collapse model of a spherical top-hat over-density the outer boundary of a halo is usually defined as a radius $R_\Delta$ enclosing a region with an over-density of $\Delta$ or more with respect to a certain reference density $\rho_{\mathrm{ref}}$, where the lower bound of the required over-density is given from the virialization criterion at the time of the virialization of the halo \citep{gunn1972infall}. However, \citet{diemer2013pseudo} found that such a boundary definition can lead to pseudo-evolution of the halo mass, meaning an apparent growth of the halo mass that is caused only by the evolution of the reference density with redshift and not by a physical accretion of mass onto the halo. Using simulations they showed that pseudo evolution accounts for nearly all of the apparent growth between $z=1$ and $0$ of galaxy-sized halos and can also account for a substantial fraction of the growth of cluster-sized halos \citep{diemer2013pseudo}. Further, \citet{diemer2013pseudo} realized that a new definition for the boundary of halos is required which must not suffer from pseudo-evolution. \citet{more2015splashback} proposed to use the newly discovered splashback radius as such an alternative definition. They found that depending on the accretion rate of the halo, the splashback radius may be well beyond the commonly used virial radius. For quickly accreting halos the splashback radius is expected to occur at $\approx 0.8-1$ $r_{\mathrm{200m}}$ and at $\approx 1.5$ $r_{\mathrm{200m}}$ for slowly accreting halos \citep{more2015splashback}.

%Cross-correlating the Sloan Digital Sky Survey (SDSS) Data Release 8 (DR8) photometric galaxy catalog with clusters identified from the SDSS DR8 catalog by the redMaPPer algorithm \citep{rykoff2014redmapper,rozo2015redmapper} \citet{more2016detection} presented evidence for the existence of the splashback radius in observations. By studying the stacked surface density profiles of the galaxy clusters they detected a sharp steepening providing strong evidence for the existence of the splashback effect.

%\citet{more2016detection} compared their findings with simulations by utilizing the MultiDark-Planck II N-body simulation \citep{klypin2016multidark}. The comparison showed that the splashback radii detected are smaller than expected from the simulation. They explored several systematic effects which could lead to such deviations. However, none of the investigated, systematic effects can account for the discrepancies found in the data.

@@

%what 3 techniques???

@@

    \begin{tabular}{ccccccccc}

@@

    & $\log_{10}(\rho_{\mathrm{s}})$ & $\log_{10}(\alpha)$ & $\log_{10}(r_{\mathrm{s}})$ & $\rho_0$ & $s_{\mathrm{e}}$ & $\log_{10}(r_{\mathrm{t}})$ & $\log_{10}(\beta)$ & $\log_{10}(\gamma)$ \\ 

@@

    %$\mathrm{Var}_{\mathrm{init}}$ & 0.8 & 0.030 & 0.058 & $4.7\cdot10^{-6}$ & $3.8\cdot10{-7}$ & 0.0088 & 0.25 & 0.0078\\ 
    %\hline 
    Prior Type & None & Normal & Flat & None & None & Flat & Normal & Normal\\ 

@@

    Prior Range & - & $\log_{10}(0.2)| 1.2$ & [0.1,5.0] & - & - & [0.1,5.0] & $\log_{10}(6.0) | 0.4$ & $\log_{10}(4.0) | 0.4$\\

@@

We restrict ourselves to the redshift range $0.03 \leq z \leq 0.33$
in order to mimic the redshift range used by
\citet{more2016detection}. Due to the large beam size of the Planck
satellite, the cluster positions as reported in the catalog may be
mis-centered from the true center of the galaxy clusters. We perform
a visual inspection of Pan-STARRS images taken around the detected
galaxy clusters in order to locate the nearest, brightest cluster
galaxy (BCG). We regard the position of the BCG as the true cluster
location, under the assumption that the BCG is located at the true,
gravitational center. The final sample that we use consists of 596
galaxy clusters and is about an order of magnitude smaller compared
to the sample used in \citet{more2016detection}. The sample we use
in this paper has an average redshift of 0.177, and an average
cluster mass $M_{500c}$ of about $3.0 \cdot 10^{14}
h^{-1}$M$_{\sun}$. In Table~\ref{tab:cluster_catalogs} we compare
the main properties of the cluster catalog used in this work to that
used by \citet{more2016detection}. The sky positions of the clusters
can be found in Figure~\ref{fig:planck_fig} in
Appendix~\ref{sec:figures}.

@@

%However, at the same time it has to be assumed that there will also be a
%population of uncorrelated galaxies present consisting of higher or lower
%redshift galaxies that are not associated with the cluster in question. The
%same holds true for the cluster population as well. Such contaminations can be
%estimated by the use of random catalogs modeling the uncorrelated component of
%the two-point cross-correlation function. We outline this procedure in
%Section~\ref{sec:est_surf_den}.  Exploiting this analysis for each one of the
%three catalogs with depth 21.0, 21.5 and 22.0 magnitude, respectively we obtain
%three different estimates of the surface density distribution in total.

%The splashback radius manifests itself as a sharp steepening in the spatial density profile of a dark matter halo. Unfortunately, such profiles are not directly accessible through measurements. However, in the standard paradigm of structure formation it is assumed that galaxies track the underlying dark matter distribution since they form from baryonic matter falling into the potential wells created by the dark matter \citep{rees1977cooling,white1978core,fall1980formation,blumenthal1984formation}. Therefore, we use the radial galaxy distribution as a proxy for the dark matter distribution of a halo. A further complication arises by the fact that only the projected galaxy distribution within a halo is accessible as a projection of the three dimensional distribution onto a projection plane perpendicular to the line of sight. Therefore, the three dimensional model given in Equation~\ref{eq:model} needs to be integrated along the line of sight in order to obtain a model for the surface density profile:

We use the functional form of \citet{diemer2014dependence} in order
to model our two-dimensional correlation function measurements. This
functional form consists of an inner Einasto profile and an outer
power law profile connected by a smooth transition
\begin{align}
\xi_{\rm 3D}(r) &= \rho_{\mathrm{in}}(r)f_{\mathrm{trans}}(r) + \rho_{\mathrm{out}}(r)\,, \\
\rho_{\mathrm{in}}(r)&=\rho_{\mathrm{s}}\exp\left( -\frac{2}{\alpha}\left[ \left( \frac{r}{r_{\mathrm{s}}}\right)^{\alpha}-1 \right] \right)\,,\\
\rho_{\mathrm{out}}(r)&=\rho_{\mathrm{0}}\left( \frac{r}{r_{\mathrm{out}}}\right)^{-s_{\mathrm{e}}} \,,\label{eq:model} \\
f_{\mathrm{trans}}(r)&=\left( 1+\left( \frac{r}{r_{\mathrm{t}}} \right)^{\beta} \right)^{-\gamma/ \beta}\,,
\label{eq:dk14}
\end{align}
where $r$ indicates the three-dimensional radial distance from the
halo center \citep{diemer2014dependence}. We model the
two-dimensional correlation function, $\xi_{\rm 2D}$ as an integral
over the three-dimensional correlation function
\begin{equation}
\xi_{\rm 2D}(R)=\frac{1}{R_{\rm max}}\int^{R_{\mathrm{max}}}_0 \xi_{\rm 3D}(\sqrt{R^2+x^2}) dx \,
\label{eq:surface}
\end{equation}
where we adopt $R_{\mathrm{max}}=40$ $h^{-1}$Mpc for the maximum projection
length. Variations of this length do not change the location of the
splashback radius appreciably as tested in
\citet{more2016detection}. The functional form adopted in
Equation~\ref{eq:dk14} has nine model parameters,
$\rho_{\mathrm{s}}, \alpha, r_{\mathrm{s}}, r_{\mathrm{out}},
\rho_{\mathrm{0}}, s_{\mathrm{e}}, r_{\mathrm{t}}, \beta$ and
$\gamma$. Given the perfect degeneracy between the parameters
$r_{\mathrm{out}}$ and $\rho_{\rm o}$, we fix $r_{\mathrm{out}}=1.5$ $
h^{-1}$Mpc and infer the posterior distribution of the remaining
eight parameters from the measurements. We use the affine invariant
Markov Chain Monte Carlo sampler of \citet{goodman2010ensemble} as
implemented in the parallel python package {\it emcee} by
\citet{foreman2013emcee}. We adopt priors similar to
\citet{more2016detection} on some of our parameters based on the
expectations of their values from numerical simulations, but double
the scales of the normal priors compared to their work (see
Table~\ref{tab:priors}). The central value for the prior on $\alpha$
is deduced from mass estimates \citep{gao2008redshift}, whereas the
central values on the priors of $\beta$ and $\gamma$ were
recommended by \citet{diemer2014dependence}.

@@

%where the function $D(z)$ determines the comoving distance to an object at redshift $z$. Further $z_{\mathrm{max}}$ is the maximal redshift of the cluster catalog (0.33 in our case) and $m_{\mathrm{lim}}$ indicates the depth of the galaxy catalog in consideration in magnitudes (being 21.0, 21.5 and 22.0, respectively) \citep{more2016detection}.
%The assigned galaxies are then binned into 8 equally spaced radial bins ranging from 0.1 h$^{-1}$ Mpc to 10 h$^{-1}$ Mpc.  
%
%We expect a correlation between clusters and galaxies if they are at the same redshift. However, at the same time it has to be assumed that there will also be a population of uncorrelated galaxies present consisting of higher or lower redshift galaxies that are not associated with the cluster in question. The same holds true for the cluster population as well. Such contaminations can be estimated by the use of random catalogs modeling the uncorrelated component of the two-point cross-correlation function. We outline this procedure in Section~\ref{sec:est_surf_den}.
%Exploiting this analysis for each one of the three catalogs with depth 21.0, 21.5 and 22.0 magnitude, respectively we obtain three different estimates of the surface density distribution in total.
%
%\subsection{Locating the splashback radius}
%\label{sec:MCMC}
%Having an estimate of the surface density function at hand we now turn to the problem of inferring the location of the splashback radius. With that goal in mind we fit the model for the surface density profile given in Equation~\ref{eq:surface} to the estimated profile. Fixing $r_{\mathrm{out}}=1.5 $ h$^{-1}$Mpc due to its full degeneracy with the parameter $\rho_{\mathrm{0}}$ this task involves fitting a model with eight free parameters namely $\rho_{\mathrm{s}}, \alpha, r_{\mathrm{s}}, \rho_{\mathrm{0}}, s_{\mathrm{e}}, r_{\mathrm{t}}, \beta$ and $\gamma$. 
%Performing a simple Least Square fit we obtain the set of parameter values as shown in Table~\ref{tab:inits}. We use the Python implementation \textit{emcee} \citep{foreman2013emcee} of the affine invariant Markov Chain Monte Carlo (MCMC) sampler of Goodman \& Weare to sample from the posterior distributions of the model parameters \citep{goodman2010ensemble}. Twenty MCMC chains are being run for 50'000 iterations each where the Least Square fitting parameters listed in Table~\ref{tab:inits} serve as their initial parameters. 
%The priors constraining the MCMC chains during the runs are listed in Table~\ref{tab:priors}. We adapt similar priors as in the work of \citet{more2016detection} but increase the scales of the normal priors allowing the chains to explore a larger fraction of the parameter space. The central value for the prior on $\alpha$ is deduced from mass estimates from weak lensing \citep{gao2008redshift} whereas the cenral values for the priors of $\beta$ and $\gamma$ were recommended by \citet{diemer2014dependence}.
%Several statistical tests are performed to confirm the convergence of the MCMC chains. The tests and their results are presented in Appendix~\ref{sec:convergence}. Given the posterior distributions of the model parameters an estimate of the three dimensional model as given in Equation~\ref{eq:model} can be constructed as well. 
%We define the splashback radius as being located at the steepest logarithmic slope of the density profile. For each measurement two different estimates of the splashback radius can be inferred; a projected splashback radius $R_{\mathrm{sp}}^{\mathrm{2D}}$ is obtained from the location of the steepening feature in the two dimensional surface density and a three dimensional, physical splashback radius $r^{\mathrm{3D}}_{\mathrm{sp}}$ is inferred from the three dimensional density profile alike. Note that according to \citet{diemer2014dependence} those two estimates are expected to differ from each other.
%Since the analytical models are known we derive the analytical expressions of the projected as well as the three dimensional logarithmic derivatives of the models using simple algebra to be
%\begin{align}
%\frac{\mathrm{d}\log(\xi )}{\mathrm{d}\log(R)}=\frac{-1}{\int_0^{z_{\mathrm{max}}}\rho (y)\mathrm{dz}} \int_0^{z_{\mathrm{max}}}\frac{R^2}{y}\left[ h(y)+ \frac{s_{\mathrm{e}}}{y}\rho_{\mathrm{out}}(y)\right]\mathrm{dz}   \\
%\frac{\mathrm{d}\log(\rho)}{\mathrm{d}\log(r)}=-\frac{r}{\rho(r)}h(r)-s_{\mathrm{e}}\frac{\rho_{\mathrm{out}}(r)}{\rho(r)}
%\end{align}
%where
%\begin{align}
%y(R,z)=\sqrt{R^2+z^2} \\
%h(x)=\rho_{\mathrm{in}}(x) \cdot f_{\mathrm{trans}}(x) \left( 2\frac{x^{\alpha -1}}{r_{\mathrm{s}}^{\alpha }}+\gamma \frac{x^{\beta -1}}{r_{\mathrm{t}}^{\beta }}\frac{1}{1+\left( \frac{x}{r_{\mathrm{t}}}\right)^{\beta }} \right)
%\end{align}
%and interpret their minima as the location of the projected and three dimensional splashback radius, respectively.
